Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Remove commented text
Small variable name updates

% We restrict ourselves to the simulation m12i \citep[first introduced
% in][]{2016ApJ...827L..23W}. For this work, this galaxy is the best-case
% scenario. It does not contain a bar (like \texttt{m12m}) or companion galaxy,
% and by eye is the closest to axisymmetric of the three galaxies presented in
% \citet{2018arXiv180610564S} \citep{2018MNRAS.481.4133G}.

@@

Suppose an open cluster of mass $M_c$ on an orbit with actions $\bm{J}_c$ is
disrupted, and that the cluster is currently at an orbit phase of
$\bm{\theta}_0$. We would like to determine all stars in the {\em Gaia}
dataset\footnote{This is likely to be more successful with DR3/4 than DR2,
since upcoming data releases will contain a far greater number of stars with
radial velocities --- though targeted, follow-up radial velocity surveys may
allow this program to be performed sooner.} that are likely to be ejected
members from that cluster. One could proceed by integrating the cluster's
orbit and selecting all stars within a certain distance of that orbit,
accounting for the fact that the stream will not exactly follow the orbit of
the cluster \citep[e.g.][]{2011MNRAS.413.1852E}.

@@

To explore the magnitude of this effect, we consider the following program.
First, we assume a cluster mass $m$ and estimate the expected action-space
dispersion from Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the $z$ offset necessary in
order for the induced error in the vertical action to be the same as the
expected action-space dispersion. If this were the case, an observer would
have to account for the different midplane of the field star and the cluster.
We repeat this analysis for each of the three orbits considered in
Section~\ref{ssec:quant}.

>>>>

@@

Suppose an open cluster of mass $m_c$ on an orbit with actions $\bm{J}_c$ is
disrupted, and that the cluster is currently at an orbit phase of
$\bm{\theta}_0$. We would like to determine all stars in the {\em Gaia}
dataset\footnote{This is likely to be more successful with DR3/4 than DR2,
since upcoming data releases will contain a far greater number of stars with
radial velocities --- though targeted, follow-up radial velocity surveys may
allow this program to be performed sooner.} that are likely to be ejected
members from that cluster. One could proceed by integrating the cluster's
orbit and selecting all stars within a certain distance of that orbit,
accounting for the fact that the stream will not exactly follow the orbit of
the cluster \citep[e.g.][]{2011MNRAS.413.1852E}.

@@

To explore the magnitude of this effect, we consider the following program.
First, we assume a cluster mass $m_c$ and estimate the expected action-space
dispersion from Equation~\ref{eq:action_disp}. We then consult
Figure~\ref{fig:many_orbit_wrong_ref} to determine the $z$ offset necessary in
order for the induced error in the vertical action to be the same as the
expected action-space dispersion. If this were the case, an observer would
have to account for the different midplane of the field star and the cluster.
We repeat this analysis for each of the three orbits considered in
Section~\ref{ssec:quant}.
